---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color:#F0F0F0;
  font-family; Arial, sans-serif;
  font-size: 20px;
  line-height: 3
}

p {
  color: #00008B;
  font-size: 20px;
  line-height: 1.5
  }
```

## TradeMe Rental Listings Tracker for Auckland's North Shore

This tracker records the rental listings of Auckland's North Shore on TradeMe, collecting data on weekly rent, property type, number of bedrooms, bathrooms, and parking spaces to provide a general view of the rental market in the North Shore. It specifically looks into the overall rent and the median rent by bedroom count and property type.

```{r}
library(tidyverse)

# read file
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTgUFRQ_Bx5MaYo2MDXQ_Q_P654WXfT5U4OSqDHknn9urqe2eXM003k3Br95va-Q6YP5l9rLVYAPAQa/pub?output=csv")

# rename variables
latest_data <- logged_data %>%
  rename(type = 2,
         rent = 3, 
         bedroom = 4, 
         bathroom = 5, 
         parking = 6)

# calculate rent statistic
max_rent <- max(latest_data$rent,na.rm = TRUE)
min_rent <- min(latest_data$rent, na.rm = TRUE)
median_rent <- median(latest_data$rent, na.rm = TRUE)

# create a new data frame called median_rent_data
# calculate median rent of property with different bedrooms
median_rent_data <- latest_data %>%
  group_by(bedroom) %>%
  summarise(median_rent = median(rent, na.rm = TRUE))

# plot bar chart according to property types
type_plot <- ggplot(latest_data, aes(x = type)) +
  geom_bar(fill = "lightgreen") +
  labs(title = "The type of Rental Property", 
       caption = "Figure 1. Bar chart showing the type of rental property.",
       x = "Rental type") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.caption = element_text(hjust = 0.5, size = 10, face = "bold")) +
  scale_y_continuous(expand = c(0, 0))


# plot bar chart according to median rent and bedrooms
median_rent_plot <- ggplot(median_rent_data, aes(x = factor(bedroom), y = median_rent)) +
  geom_bar(stat = "identity", fill = "pink") +
  labs(title = "Median Rent by Number of Bedrooms",
       caption = "Figure 2. Bar chart showing the median weekly rent according to the number of bedrooms.",
       x = "Number of Bedrooms",
       y = "Median Rent ($/week)") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.caption = element_text(hjust = 0.5, size = 10, face = "bold")) +
  scale_y_continuous(expand = c(0, 0))


# plot scatter plot according to rent and bedrooms
rent_plot <- ggplot(latest_data, aes(x = bedroom, y = rent)) + 
  geom_point(alpha = 0.7, color = "blue", shape = 23, size = 3) +
  labs(title = "Rent vs.Number of Bedrooms", 
       caption = "Figure 3. Scatter plot showing the relationship between the number of bedrooms and weekly rent.",
       x = "Number of Bedrooms",
       y = "Rent ($/week)") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        plot.caption = element_text(hjust = 0.5, size = 10, face = "bold"))
```

***The highest weekly rent in Auckland's North Shore is $`r max_rent`, the lowest is $`r min_rent`, and the median is $`r median_rent`.***

The type of rental property in Auckland's North Shore:

```{r, echo=FALSE}
type_plot 
```

The median rent of property with different bedrooms:

```{r, echo=FALSE}
median_rent_plot
```

The rent of property with different bedrooms:

```{r, echo=FALSE}
rent_plot
```
